\input{title.tex}

### 2022-05-01 docs/papers/01_manuscript/01_introduction.tex
feat(new-plot-fig-3): re-draw fig 3
BREAKING CHANGE:

% 黄河的介绍
The Yellow River Basin (YRB), the fifth large river worldwide, is known for its irreplaceable role in the social-economic development of China, and thus also drastically interference by anthropogenic stress.
Supporting $35.63\%$ irrigation and $30\%$ population with only $2.66\%$ water resources of China (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: 28 February 2021), the overburdened Yellow River dried up in consecutive years, resulting in substantial ecological, economic and social crisis (e.g., wetland shrink, agriculture reduction, and scramble for water).
Intense water use, accounting for about $80\%$ of Yellow River surface runoff in the 1980s, was remarked as the significant reason for the degradation.
Furthermore, human interferences such as soil conservation and water conservancy project boosted water withdrawal and then stressed the water scarcity of the Yellow River.
In the context of future climate change, the contradiction between supplies and demands of water resources in the YRB will become more prominent.
%! Citation: Hao Wang presentation.
Therefore, balancing ecological and developing demands in such a human-dominated basin is a problem for China in water governance throughout and for large rivers worldwide.

% 第三段 过去管理的经验，断流的严重程度，连续多少没有断流，少有的解决断流的大河。治理成功的流域？分析背后的机制，基础。往用水上靠。
% 为了缓解用水压力
Chinese authorities implemented several ambitious water management practices in the YRB in the last century to relieve the water stress, such as reservoir regulation, South-to-north Water Diversion Project (WDP), and Water Allocation Scheme since 1987 (87-WAS), and the Unified Basinal Regulation since 1998 (98-UBR).
Through those efforts, ecological restoration of wetland and estuary delta in the YRB without drying up for over $20$ is widely considered a considerable river management achievement.
Different from the engineering of WDP provides further water supply or reservoir matches water supply and demands, institutional strategies like the 87-WAS (assign water quotas for provinces in the YRB) and the 98-UBR (the provinces had to be allowed for using water by the Yellow River Conservancy Commission, YRCC) mainly focused on limiting demands of water use.
Such institutions (policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled human, and natural system, including interplays between social actors, ecological units, or between social and ecological system elements \cite{young2008,cumming2020b,lien2020, bodin2017b}.
Understanding those complex interlinkages, therefore, is crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems (SES) \cite{kluger2020}.
However, while literature had well evaluated and quantified the effects of engineering solutions beforehand, there are few attempts to assess institutional contributions to successful water governance.

>>>>

% 黄河的介绍
The Yellow River Basin (YRB), the fifth large river worldwide, is known for its irreplaceable role in the social-economic development of China, and thus also drastically interference by anthropogenic stress.
Supporting $35.63\%$ irrigation and $30\%$ population with only $2.66\%$ water resources of China (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: 28 February 2021), the overburdened Yellow River dried up in consecutive years, resulting in substantial ecological, economic and social crisis (e.g., wetland shrink, agriculture reduction, and scramble for water).
Intense water use, accounting for about $80\%$ of Yellow River surface runoff in the 1980s, was remarked as the significant reason for the degradation.
Furthermore, human interferences such as soil conservation and water conservancy project boosted water withdrawal and then stressed the water scarcity of the Yellow River.
In the context of future climate change, the contradiction between supplies and demands of water resources in the YRB will become more prominent.
%! Citation: Hao Wang presentation.
Therefore, balancing ecological and developing demands in such a human-dominated basin is a problem for China in terms of water governance throughout and for large rivers worldwide.

% 第三段 过去管理的经验，断流的严重程度，连续多少没有断流，少有的解决断流的大河。治理成功的流域？分析背后的机制，基础。往用水上靠。
% 为了缓解用水压力
Chinese authorities implemented several ambitious water management practices in the YRB in the last century to relieve the water stress, such as reservoir regulation, South-to-north Water Diversion Project (WDP), and Water Allocation Scheme since 1987 (87-WAS), and the Unified Basinal Regulation since 1998 (98-UBR).
Through those efforts, ecological restoration of wetland and estuary delta in the YRB without drying up for over $20$ is widely considered a considerable river management achievement.
Different from the engineering of WDP provides further water supply or reservoir matches water supply and demands, institutional strategies like the 87-WAS (assign water quotas for provinces in the YRB) and the 98-UBR (the provinces had to be allowed to use water by the Yellow River Conservancy Commission, YRCC) mainly focused on limiting demands of water use.
Such institutions (policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled human and natural system, including interplays between social actors, ecological units, or between social and ecological system elements \cite{young2008,cumming2020b,lien2020, bodin2017b}.
Understanding those complex interlinkages, therefore, is crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems (SES) \cite{kluger2020}.
However, while literature had well evaluated and quantified the effects of engineering solutions beforehand, there are few attempts to assess institutional contributions to successful water governance.

### 2022-05-01 docs/papers/01_manuscript/04_discussion.tex
feat(new-plot-fig-3): re-draw fig 3
BREAKING CHANGE:

% 过去的研究总结出87-WAS收效甚微的几个因素：
Although previous studies summarised reasons for the non-ideal effect of 87-WAS, few improvements in the 98-UBR indicate that they underestimated influences from the structural changes (\textit{S3 in Supplementary Material} Figure~\ref{fig:ref{S3-3}}).
As we have depicted (Figure~\ref{structure}), the institutional shifts twice framed the structure of SESs in the YRB and led to different building blocks, which were also reported in various types of SESs worldwide.
The empirical studies in many different fields also indicate that the structure before 98-UBR (i.e., fragment ecological units are linked to separate social actors) is likely to be mismatched as isolated stakeholders struggle with holistically maintaining interconnected ecosystems
\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
On the contrary, the YRCC, whose authority matched the YRB in scale after the 98-UBR, led to a well-recognized structure for institutional alignments to social-ecological fit and good outcomes.
The effect of the institutional shifts once again demonstrated that it is not easy to have a win-win situation of environment and interests in complex coupled human-nature systems \cite{hegwood2022} which calls for exceptional understanding and caution to the structure of hampering sustainability \cite{bergsten2019, sayles2019}.

>>>>

% 过去的研究总结出87-WAS收效甚微的几个因素：
Although previous studies summarised reasons for the non-ideal effect of 87-WAS, few improvements in the 98-UBR indicate that they underestimated influences from the structural changes (\textit{S3 in Supplementary Material} Figure~\ref{fig:{S3-3}).
As we have depicted (Figure~\ref{structure}), the institutional shifts twice framed the structure of SESs in the YRB and led to different building blocks, which were also reported in various types of SESs worldwide.
The empirical studies in many different fields also indicate that the structure before 98-UBR (i.e., fragment ecological units are linked to separate social actors) is likely to be mismatched as isolated stakeholders struggle with holistically maintaining interconnected ecosystems
\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
On the contrary, the YRCC, whose authority matched the YRB in scale after the 98-UBR, led to a well-recognized structure for institutional alignments to social-ecological fit and good outcomes.
The effect of the institutional shifts once again demonstrated that it is not easy to have a win-win situation of environment and interests in complex coupled human-nature systems \cite{hegwood2022} which calls for exceptional understanding and caution to the structure of hampering sustainability \cite{bergsten2019, sayles2019}.
